ODGI: understanding pangenome graphs

### 2022-01-19 manuscript/main.tex
do not explicit that path colors are derived from a hash of the path names
Conflict of Interest
ORCIDs, enable hyperref in black

\usepackage[draft]{hyperref}
\usepackage{makecell}
\usepackage{comment}

@@

@@

\title[ODGI: understanding pangenome graphs]{ODGI: understanding pangenome graphs}
\author[Guarracino, Heumos \textit{et~al}.]{
Andrea~Guarracino\,$^{\text{\sfb 1} \dagger}$,
Simon~Heumos\,$^{\text{\sfb 2} \dagger}$,
Sven~Nahnsen\,$^{\text{\sfb 2,3}}$,
Pjotr~Prins\,$^{\text{\sfb 4}}$,
and~Erik~Garrison\,$^{\text{\sfb 4}*}$
}

@@

\textit{odgi viz} supports a binned, linearized rendering in 1 dimension (1D) (that is, all graph nodes lie on the same axis).
This visualization is computed in linear-time and offers a human-interpretable format suitable for understanding the topology and genome relationships in the pangenome graph (Fig.~\ref{fig:odgi_viz}).
Graph nodes are arranged on a single axis, from left to right, with the colored bar indicating the paths and the nodes they cross.
White spaces indicate where paths do not traverse the nodes.
The meaning of the colors depends on how \textit{odgi viz} is executed.
By default, path colors are derived from a hash of the path name (Fig.~\ref{fig:odgi_viz}\textbf{b}).
Path names are displayed on the left of the paths.
The black lines on the bottom indicate the edges connecting the nodes and, therefore, represent the graph topology.

@@

>>>>

\usepackage[]{hyperref}
\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black,citecolor=black}
\usepackage{makecell}
\usepackage{comment}

@@

\usepackage{orcidlink}

@@

\title[ODGI: understanding pangenome graphs]{ODGI: understanding pangenome graphs}
\author[Guarracino, Heumos \textit{et~al}.]{
Andrea~Guarracino\orcidlink{0000-0001-9744-131X}\,$^{\text{\sfb 1} \dagger}$,
Simon~Heumos\orcidlink{0000-0003-3326-817X},$^{\text{\sfb 2} \dagger}$
Sven~Nahnsen\orcidlink{https://orcid.org/0000-0002-4375-0691}$^{\text{\sfb 2,3}}$,
Pjotr \\Prins\orcidlink{0000-0002-8021-9162}$^{\text{\sfb 4}}$,
and~Erik~Garrison\orcidlink{0000-0003-3821-631X}$^{\text{\sfb 4}*}$
}

@@

\textit{odgi viz} supports a binned, linearized rendering in 1 dimension (1D) (that is, all graph nodes lie on the same axis).
This visualization is computed in linear-time and offers a human-interpretable format suitable for understanding the topology and genome relationships in the pangenome graph (Fig.~\ref{fig:odgi_viz}).
Graph nodes are arranged on a single axis, from left to right, with the colored bar indicating the paths and the nodes they cross.
White spaces indicate where paths do not traverse the nodes.
The meaning of the colors depends on how \textit{odgi viz} is executed.
By default, path colors are derived from the path names (Fig.~\ref{fig:odgi_viz}\textbf{b}).
Path names are displayed on the left of the paths.
The black lines on the bottom indicate the edges connecting the nodes and, therefore, represent the graph topology.

@@

\section*{Conflict of Interest}

The authors declare that they have no competing interests.
